Test if analytic derivation of geodesic distance for curves from sim_functional_data.R

### 2019-05-22 test_analytic_geodesic_distance.Rmd
updated compare_methods to work with pairwise_geoestimation

---
title: Test if analytic derivation of geodesic distance for curves from sim_functional_data.R
  is correct
output:
  pdf_document: default
  html_document:
    df_print: paged
---

@@

#use_python('/Users/suswei/anaconda3/bin/python',required=TRUE)
use_python('/Users/UQAM/anaconda3/bin/python',required=TRUE)

get_min_num_neighbors = import_from_path("get_min_num_neighbors",path='.')
getIsomapGdist = import_from_path("getIsomapGdist",path='.')

>>>>

---
title: Test if analytic derivation of geodesic distance for curves from sim_functional_data.R
  is correct
output:
  html_document:
    df_print: paged
  pdf_document: default
---

use_python('/Users/suswei/anaconda3/bin/python',required=TRUE)
#use_python('/Users/UQAM/anaconda3/bin/python',required=TRUE)
```

@@

```{r}
get_min_num_neighbors = import_from_path("get_min_num_neighbors",path='.')
getIsomapGdist = import_from_path("getIsomapGdist",path='.')
